---
output: rmarkdown::github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "inst/extdata/"
)
```

## `germinationmetrics`: Seed Germination Indices and Curve Fitting

```{r,echo = FALSE, message = FALSE}
devtools::load_all(".")

```

###### Version : [`r getNamespaceVersion("germinationmetrics")`](https://aravind-j.github.io/germinationmetrics/articles/Introduction.html#version-history); Copyright (C) 2017-2018: [ICAR-NBPGR](http://www.nbpgr.ernet.in/); License: [GPL2|GPL-3](https://www.r-project.org/Licenses/)


##### *J. Aravind, S. Vimala Devi, J. Radhamani, Sherry R. Jacob  and Kalyani Srinivasan*

ICAR-National Bureau of Plant Genetic Resources, New Delhi

***

[![minimal R version](https://img.shields.io/badge/R>%3D-3.0.2-6666ff.svg)](https://cran.r-project.org/)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version-last-release/germinationmetrics)](https://cran.r-project.org/package=germinationmetrics)
<!-- [![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/germinationmetrics?color=green)](https://CRAN.R-project.org/package=germinationmetrics) -->
<!-- [![packageversion](https://img.shields.io/badge/Package%20version-0.2.3.3-orange.svg)](https://github.com/aravind-j/germinationmetrics) -->
[![develVersion](https://img.shields.io/badge/devel%20version-`r getNamespaceVersion("germinationmetrics")`-orange.svg)](https://github.com/aravind-j/germinationmetrics)
<!-- [![GitHub Download Count](https://github-basic-badges.herokuapp.com/downloads/aravind-j/germinationmetrics/total.svg)] -->
[![Project Status: WIP](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
<!-- [![Rdoc](http://www.rdocumentation.org/badges/version/germinationmetrics)](http://www.rdocumentation.org/packages/germinationmetrics) -->
<!-- [![Zenodo DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.841963.svg)](https://doi.org/10.5281/zenodo.841963) -->
[![Analytics](https://pro-pulsar-193905.appspot.com/UA-116205606-1/welcome-page)](https://github.com/aravind-j/google-analytics-beacon)

***

## Description
`r gsub("\\n", " ", packageDescription("germinationmetrics", fields = "Description"))`

## Installation

### Install development version from Github
```{r, eval=FALSE}
devtools::install_github("aravind-j/germinationmetrics")
```

## Detailed tutorial
For a detailed tutorial on how to used this package type:

```{r, eval=FALSE}
browseVignettes(package = 'germinationmetrics')
```

## What's new
To know whats new in this version type:

```{r, eval=FALSE}
news(package='germinationmetrics')
```

## Links

## Citing `germinationmetrics`
To cite the methods in the package use:

```{r, eval = FALSE}
citation("germinationmetrics")
```

```{r, echo = FALSE}
cit <- citation("germinationmetrics")
yr <- format(Sys.Date(), "%Y")
cit[1]$year <- yr
oc <- class(cit)

cit <- unclass(cit)
attr(cit[[1]],"textVersion") <- gsub("\\(\\)",
                                     paste("\\(", yr, "\\)", sep = ""),
                                     attr(cit[[1]],"textVersion"))
class(cit) <- oc
cit
```
