---
title: "The **germinationmetrics** package: A brief introduction"
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[LE,RO]{\slshape \rightmark}
- \fancyhead[LO,RE]{An Introduction to germinationmetrics package}
- \fancyfoot[C]{\thepage}
- \usepackage{hyperref}
- \hypersetup{colorlinks=true}
- \hypersetup{linktoc=all}
- \hypersetup{linkcolor=blue}
- \usepackage{pdflscape}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document:
    dev: cairo_pdf
    fig_caption: no
  html_document:
    df_print: paged
csl: frontiers.csl
bibliography: REFERENCES.bib
toc: no
vignette: |
  %\VignetteIndexEntry{Introduction}
  %\usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown_notangle}
---
\begin{center}
 {\it J. Aravind, J. Radhamani, S. Vimala Devi and Kalyani Srinivasan}
\end{center}

\begin{center}
 ICAR-National Bureau of Plant Genetic Resources, New Delhi
\end{center}

\begin{center}
`r Sys.Date()`
\end{center}

\begin{center}
\vspace{6pt}
\hrule
\end{center}

```{r, echo = FALSE}
knitr::opts_chunk$set(
  comment = "",
  fig.cap = ""
)
```

\tableofcontents

## Overview

The package `germinationmetrics` is a collection of functions which implements various methods for describing the time-course of germination in terms of single-value germination indices as well as fitted curves.

The goal of this vignette is to introduce the users to these functions and get started in describing sequentially recorded germination count data. This document assumes a basic knowledge of `R` programming language.

## Installation
The package can be installed using the following functions:

```{r, eval=FALSE}
# Install from CRAN
install.packages('germinationmetrics', dependencies=TRUE)

```

Then the package can be loaded using the function
```{r}
library(germinationmetrics)
```

## Germination count data

Typically in a germination test, the germination count data of a fixed number of seeds is recorded at regular intervals for a definite period of time or until all the seeds have germinated. These germination count data can be either partial or cumulative (Table 1).

**Table 1 :** A typical germination count data.

```{r, echo = FALSE}
data <- data.frame(intervals = 1:14,
                   counts = c(0, 0, 0, 0, 4, 17, 10, 7, 1, 0, 1, 0, 0, 0))
data$cumulative.counts = cumsum(data$counts)

knitr::kable(data)

```

The time-course of germination can be plotted as follows:

```{r}
data <- data.frame(intervals = 1:14,
                   counts = c(0, 0, 0, 0, 4, 17, 10, 7, 1, 0, 1, 0, 0, 0))

# Partial germination counts
x <- data$counts
# Cumulative germination counts
y <- cumsum(x)
# Time intervals of observations
int <- data$intervals

plot(int, cumsum(x))
```

## Single-value germination indices

The details about the single-value germination indices implemented in `germinationmetrics` are described in Table 2.

\newpage
\blandscape

\rowcolors{2}{gray!25}{white}
\renewcommand{\arraystretch}{1.3}

**Table 2 :** Single-value germination indices implemented in `germinationmetrics`.
\footnotesize
```{r, echo = FALSE, eval = TRUE}
load("Indices.rda")

indices$`function` <- paste("`", indices$`function`, "`", sep = "")

# indices$Details <- gsub("\\r\\n\\r\\n", "$$\\\\, $$", indices$Details)
# indices$Details <- gsub("$$\\, $$$$", "$$", indices$Details, fixed = TRUE)
#indices$Details <- paste(indices$Details, "$$\\\\, $$", sep = "")

indices$Details <- gsub("\\r\\n", "\\\\\n", indices$Details)

#indices$Details <- gsub("\\r\\n\\r\\n", "##", indices$Details)
#indices$Details <- gsub("##", "\\\n", indices$Details)

indices$Reference <- gsub("\\[|\\]", "", indices$Reference)
#indices <- indices[-27,]

```


```{r, echo = FALSE, eval = TRUE}
pander::pander(indices, style='multiline',
               split.cell = c(15, 18, 50, 10, 10, 10),
               justify = c('left'), split.table = Inf, keep.line.breaks = TRUE,
               use.hyphening = FALSE, missing = "")
```

\elandscape

\newpage

#### Examples

```{r, echo = FALSE}
# Function saved in functions.R file
getCode <- function(myFunction, myPackage) {
  out <- example(myFunction, myPackage, ask = FALSE, character.only = TRUE,
          prompt.prefix = "", give.lines = TRUE)
  maxn <- grep(pattern = "### ** Examples", x = out, fixed = TRUE)
  out <- out[-(1:maxn)]
  
  return(out)
}
library("germinationmetrics")
```

#### `GermPercent()`
```{r, runCode, code = getCode("GermPercent", "germinationmetrics")}
```

#### `FirstGermTime(), LastGermTime(), PeakGermTime(), TimeSpreadGerm()`
```{r, runCode, code = getCode("FirstGermTime", "germinationmetrics")}
```

#### `t50()`
```{r, runCode, code = getCode("t50", "germinationmetrics")}
```

#### `MeanGermTime(), VarGermTime(), SEGermTime(), CVSEGermTime()`
```{r, runCode, code = getCode("MeanGermTime", "germinationmetrics")}
```

#### `MeanGermRate(), CVG(), VarGermRate(), SEGermRate(), GermRateRecip()`
```{r, runCode, code = getCode("MeanGermRate", "germinationmetrics")}
```

#### `GermSpeed(), GermSpeedAccumulated(), GermSpeedCorrected() `
```{r, runCode, code = getCode("GermSpeed", "germinationmetrics")}
```

#### `GermSpeed(), GermSpeedAccumulated(), GermSpeedCorrected() `
```{r, runCode, code = getCode("GermSpeed", "germinationmetrics")}
```

#### `MeanGermPercent(), MeanGermNumber()`
```{r, runCode, code = getCode("MeanGermPercent", "germinationmetrics")}
```

#### `TimsonsIndex(), GermRateGeorge() `
```{r, runCode, code = getCode("TimsonsIndex", "germinationmetrics")}
```

#### `PeakValue(), GermValue()`
```{r, runCode, code = getCode("PeakValue", "germinationmetrics")}
```

#### `CUGerm()`
```{r, runCode, code = getCode("CUGerm", "germinationmetrics")}
```

#### `GermSynchrony(), GermUncertainty()`
```{r, runCode, code = getCode("GermSynchrony", "germinationmetrics")}
```

## Curve fitting

Several mathematical functions have been used to fit the cumulative germination count data and describe the germination process such as Richard's, Weibull, logistic, log-logistic, gaussian, four-parameter hill function etc. Currently `germinationmetrics` implements the four-parameter hill function to fit the count data and computed various associated metrics.

### Four-parameter hill function
The four-parameter hill function defined as follows [@el-kassaby_seed_2008]:

$$
f(x) = y = y_0 + \frac{ax^b}{x^b+c^b}
$$
Where, $y$ is the cumulative germination percentage at time $x$, $y_{0}$ is the intercept on the y axis, $a$ is the asymptote, $b$ is a mathematical parameter controlling the shape and steepness of the germination curve and $c$ is the "half-maximal activation level".

The details of various parameters that are computed from this function are given in Table 3.

**Table 3** Germination parameters estimated from the four-parameter hill function.

\rowcolors{2}{gray!25}{white}
\renewcommand{\arraystretch}{1.3}
```{r, echo = FALSE, eval = TRUE}
load("Indices.rda")
fphf$Details <- gsub("\\r\\n", "\\\\\n", fphf$Details)
pander::pander(fphf, style='multiline',
               split.cell = c(15, 50, 10, 10),
               justify = c('left'), split.table = Inf, keep.line.breaks = TRUE,
               use.hyphening = FALSE, missing = "")
```

#### Examples

```{r, echo = FALSE}
# Function saved in functions.R file
getCode <- function(myFunction, myPackage) {
  out <- example(myFunction, myPackage, ask = FALSE, character.only = TRUE,
          prompt.prefix = "", give.lines = TRUE)
  maxn <- grep(pattern = "### ** Examples", x = out, fixed = TRUE)
  out <- out[-(1:maxn)]
  
  return(out)
}
library("germinationmetrics")
```

#### `FourPHFfit()`
```{r, runCode, code = getCode("FourPHFfit", "germinationmetrics")}
```

## Citing `germinationmetrics`

```{r, echo = FALSE, collapse = TRUE}
suppressMessages(cit <- citation("germinationmetrics"))
yr <- format(Sys.Date(), "%Y")
cit[1]$year <- yr
oc <- class(cit)

cit <- unclass(cit)
attr(cit[[1]],"textVersion") <- gsub("\\(\\)",
                                     paste("\\(", yr, "\\)", sep = ""),
                                     attr(cit[[1]],"textVersion"))
class(cit) <- oc
cit
```

## Session Info

```{r}
sessionInfo()
```

## References
